hbm_paper_results

### 2024-02-19 paper_main_results.Rmd

@@

intersect(gam_better$pheno, ns_gam_gamlss_comp$pheno)
```
```{r, eval=FALSE}
for (pheno in pheno_abs.diff.list){
  p <- ggplot(gam.gamlss.diffs, aes(y = gam.gamlss.diffs[[pheno]], fill= dataset)) +
      geom_boxplot() +
    ggtitle(pheno)
print(p)
}
```

>>>>

All features:
```{r}
long_abs.diffs <- diffs.df %>%
  dplyr::filter(dataset == "cf.lm" | dataset == "cf.gam" | dataset == "cf.gamlss") %>% #drop refA levels
  dplyr::select(participant, sex, age_days, sim.site, dataset, paste0("abs.diff_", pheno_list)) %>%
  pivot_longer(cols=starts_with("abs.diff_"), names_to="pheno", names_prefix="abs.diff_", values_to = "abs.diff") %>%
  mutate(dataset = factor(dataset, levels = c("ukb_CN", "cf", "cf.lm", "cf.gam", "cf.gamlss"), ordered = TRUE),
         abs.diff = abs.diff*100,
         pheno_cat = as.factor(case_when(
      pheno %in% vol_list_global ~ "Global Volume",
      pheno %in% vol_list_regions ~ "Regional Volume",
      pheno %in% sa_list ~ "Regional SA",
      pheno %in% ct_list ~ "Regional CT",
      TRUE ~ NA_character_)))

long_abs_diff.plt <- long_abs.diffs %>%
  ggplot(aes(pheno, abs.diff)) +
  geom_violin(aes(x=pheno, y=abs.diff, fill=dataset, color=dataset), scale="count") +
  theme_linedraw(base_size = 11) +
  scale_fill_manual(values=c(cf.gam = "#3D75C2", cf.lm = "#75C23D", cf.gamlss ="#CFB023FF"), name = "ComBat \nConfiguration", labels=dataset_names) +
  scale_color_manual(values=c(cf.gam = "#3D75C2", cf.lm = "#75C23D", cf.gamlss ="#CFB023FF"), name = "ComBat \nConfiguration", labels=dataset_names) +
  labs(y="Absolulte Centile Error", x = "Feature") +
  theme(plot.title = element_text(size=12), axis.text.x = element_text(angle = 90, vjust=0.4, size=6), legend.position="top") +
  facet_wrap(~pheno_cat, nrow=4, scales="free")
ggsave("figs/all_abs_err_plt_wlabels.jpeg", long_abs_diff.plt, width=13, height=10.5, units="in")

long_abs.diffs %>%
  dplyr::filter(dataset == "cf.gam" | dataset == "cf.gamlss") %>%
  ggplot(aes(pheno, abs.diff)) +
  geom_violin(aes(x=interaction(pheno,pheno_cat, sep = "&"), y=abs.diff,  fill=dataset, color=dataset), scale="count") +
  theme_linedraw(base_size = 11) +
  scale_fill_manual(values=c(cf.gam = "#3D75C2", cf.lm = "#75C23D", cf.gamlss ="#CFB023FF"), name = "ComBat \nConfiguration", labels=dataset_names) +
  scale_color_manual(values=c(cf.gam = "#3D75C2", cf.lm = "#75C23D", cf.gamlss ="#CFB023FF"), name = "ComBat \nConfiguration", labels=dataset_names) +
  labs(y="Absolulte Centile Error", x = "Feature") +
  guides(x = ggh4x::guide_axis_nested(delim = "&")) +
  theme(plot.title = element_text(size=12), axis.text.x = element_text(angle = 90, vjust=0.4, size=6), ggh4x.axis.nesttext.x = element_text(angle = 90, vjust=0.4), legend.position="top")

# ggsave("figs/global_centile_errors.jpeg", global_cent_errs_plot)
```

@@

cfgam.better <- intersect(gam_better$pheno, ns_gam_gamlss_comp$pheno)
```
```{r, eval=FALSE}
cfgam.better.ct <- gsub("_CT", "", cfgam.better)
cfgam.better.ct_plot <- dk.parc %>%
  dplyr::mutate(gam_better = ifelse(label %in% cfgam.better.ct, 1, 0))

ggplot(cfgam.better.ct_plot) +
  theme_linedraw(base_size=12) +
  ggseg::geom_brain(atlas = dk_nomed, 
             position = position_brain(hemi ~ side),
            aes(fill=as.factor(gam_better)))
```

```{r, eval=FALSE}
for (pheno in pheno_abs.diff.list){
  p <- ggplot(gam.gamlss.diffs, aes(y = gam.gamlss.diffs[[pheno]], fill= dataset)) +
      geom_boxplot() +
    ggtitle(pheno)
print(p)
}
```

### 2024-02-19 paper_replication_results.Rmd

```{r}
ct.t.tests <- cent.feat.t.test.df %>%
  dplyr::filter(comp =="cf.gamlss_cf.gam" & stringr::str_detect(pheno, "CT")) %>%
  mutate(label=gsub("_CT", "", pheno),
         worsefit = ifelse(sig_fdr==TRUE, bigger_group, "NS"))

@@

ct.t.tests_to_plt %>%
  ggplot() +
  theme_linedraw(base_size=12) +
  ggseg::geom_brain(atlas = dk_nomed, 
             position = position_brain(hemi ~ side),
            aes(fill=worsefit)) +
  theme(axis.title = element_blank(), axis.text = element_blank(), axis.ticks = element_blank(), panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.border = element_rect(color= "gray", fill = NA), aspect.ratio=, plot.margin = margin(1,1,1,1, 'pt'), strip.text.y = element_blank()) +
  facet_wrap(~perm, nrow=2)
```

>>>>

```{r}
ct.t.tests <- cent.feat.t.test.df %>%
  dplyr::filter(comp =="cf.gamlss_cf.gam" & stringr::str_detect(pheno, "CT")) %>%
  mutate(label=gsub("_CT", "", pheno),
         better_fit = case_when(sig_fdr==TRUE & bigger_group == "cf.gam" ~ "cf.gamlss",
                              sig_fdr==TRUE & bigger_group == "cf.gamlss" ~ "cf.gam",
                              sig_fdr==FALSE ~ "NS"))

@@

ct.t.tests_to_plt %>%
  ggplot() +
  theme_linedraw(base_size=12) +
  ggseg::geom_brain(atlas = dk_nomed, 
             position = position_brain(hemi ~ side),
            aes(fill=better_fit)) +
  theme(axis.title = element_blank(), axis.text = element_blank(), axis.ticks = element_blank(), panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.border = element_rect(color= "gray", fill = NA), aspect.ratio=, plot.margin = margin(1,1,1,1, 'pt'), strip.text.y = element_blank(),
        legend.position="top") +
  scale_fill_manual(values = c(NS= "darkgray", cf.gam = "#3D75C2", cf.gamlss ="#CFB023FF"), name = "Better ComBat Method") +
  facet_wrap(~perm, nrow=2)
```
